---
title: "Regionally Integrated Time Series Analysis"
author: Stevie Walker
output: html_notebook
---

REGIONAL TIME SERIES ANALYSIS

1. Calculate MLDmax and EZ depth arrays from regridded data for making time series
```{r}

setwd("~/senior_thesis/")
source('libraries.R')
setwd("~/regional_time_series_analysis/code")
source('calc_rg_time_series_MLDmax.R')
source('calc_rg_time_series_EZ_depth.R')

models = c("CESM", "CM4", "CMCC", "EC-Earth", "GFDL", "IPSL", "MPI", "UKESM")

lapply(models, rg_time_series_MLDmax)

models = c("CESM", "CM4", "CMCC", "EC-Earth", "GFDL", "IPSL", "MPI")

lapply(models, rg_time_series_ez_depth, UKESM.file = NA)

#must run in chunks since UKESM NPP file is too big to combine
rg_time_series_ez_depth(model.name = "UKESM", UKESM.file = 1)
rg_time_series_ez_depth(model.name = "UKESM", UKESM.file = 2)
rg_time_series_ez_depth(model.name = "UKESM", UKESM.file = 3)
rg_time_series_ez_depth(model.name = "UKESM", UKESM.file = 4)
rg_time_series_ez_depth(model.name = "UKESM", UKESM.file = 5)

```


2. Calculate area of each region and historical and long-term fluxes
The area sums come from GFDL regridded data, calc_GFDL_region_area.R
```{r}
setwd("~/regional_time_series_analysis/code")
source('calc_GFDL_region_area.R')
source('calc_regional_time_series_averages.R')

calc_region_sum(DH = "POC_100")
calc_region_sum(DH = "POC_1000")
calc_region_sum(DH = "POC_MLDmax")
calc_region_sum(DH = "POC_PCD")
calc_region_sum(DH = "POC_EZ")
calc_region_sum(DH = "NPP")

```
Per area flux = Pg C/m2/yr
Total flux = Pg C/yr

2. Calculate regional POC flux time series at 100m
```{r}

setwd("~/senior_thesis/")
source('libraries.R')
setwd("~/regional_time_series_analysis/code/")
source('calc_regional_time_series_epc100.R')
source('calc_regional_time_series_expc.R')

models = c("CESM","CMCC", "EC-Earth", "GFDL", "IPSL", "MPI", "UKESM")
regions = c("SO_50", "SO_60", "30_low_lats", "15_low_lats","EQ_Pacific", "low_lats_no_EQ_Pacific", "North_Atlantic")


lapply(models, regional_ts_100, region = "SO_50")
lapply(models, regional_ts_100, region = "SO_60")
lapply(models, regional_ts_100, region = "30_low_lats")
lapply(models, regional_ts_100, region = "15_low_lats")
lapply(models, regional_ts_100, region = "North_Atlantic")
lapply(models, regional_ts_100, region = "EQ_Pacific")
lapply(models, regional_ts_100, region = "low_lats_no_EQ_Pacific")
#run from calc_regional_time_series_expc function because this model doesn't archive at 100m
lapply(regions, regional_ts_expc, model.name = "CM4", DH = 100)

#code for if you need to run a model individually -------

regional_ts_expc(model.name = "CM4", region = "SO_60", DH = 100)
regional_ts_expc(model.name = "CM4", region = "SO_50", DH = 100)
regional_ts_expc(model.name = "CM4", region = "North_Atlantic", DH = 100)
regional_ts_expc(model.name = "CM4", region = "30_low_lats", DH = 100)
regional_ts_expc(model.name = "CM4", region = "15_low_lats", DH = 100)
regional_ts_expc(model.name = "CM4", region = "EQ_Pacific", DH = 100)
regional_ts_expc(model.name = "CM4", region = "low_lats_no_EQ_Pacific", DH = 100)

regional_ts_100(model.name = "CESM", region = "SO_60")
regional_ts_100(model.name = "CMCC", region = "SO_60")
regional_ts_100(model.name = "EC-Earth", region = "SO_60")
regional_ts_100(model.name = "GFDL", region = "SO_60")
regional_ts_100(model.name = "IPSL", region = "SO_60")
regional_ts_100(model.name = "MPI", region = "SO_60")
regional_ts_100(model.name = "UKESM", region = "SO_60")

regional_ts_100(model.name = "CESM", region = "SO_50")
regional_ts_100(model.name = "CMCC", region = "SO_50")
regional_ts_100(model.name = "EC-Earth", region = "SO_50")
regional_ts_100(model.name = "GFDL", region = "SO_50")
regional_ts_100(model.name = "IPSL", region = "SO_50")
regional_ts_100(model.name = "MPI", region = "SO_50")
regional_ts_100(model.name = "UKESM", region = "SO_50")

regional_ts_100(model.name = "CESM", region = "North_Atlantic")
regional_ts_100(model.name = "CMCC", region = "North_Atlantic")
regional_ts_100(model.name = "EC-Earth", region = "North_Atlantic")
regional_ts_100(model.name = "GFDL", region = "North_Atlantic")
regional_ts_100(model.name = "IPSL", region = "North_Atlantic")
regional_ts_100(model.name = "MPI", region = "North_Atlantic")
regional_ts_100(model.name = "UKESM", region = "North_Atlantic")

regional_ts_100(model.name = "CESM", region = "30_low_lats")
regional_ts_100(model.name = "CMCC", region = "30_low_lats")
regional_ts_100(model.name = "EC-Earth", region = "30_low_lats")
regional_ts_100(model.name = "GFDL", region = "30_low_lats")
regional_ts_100(model.name = "IPSL", region = "30_low_lats")
regional_ts_100(model.name = "MPI", region = "30_low_lats")
regional_ts_100(model.name = "UKESM", region = "30_low_lats")

regional_ts_100(model.name = "CESM", region = "EQ_Pacific")
regional_ts_100(model.name = "CMCC", region = "EQ_Pacific")
regional_ts_100(model.name = "EC-Earth", region = "EQ_Pacific")
regional_ts_100(model.name = "GFDL", region = "EQ_Pacific")
regional_ts_100(model.name = "IPSL", region = "EQ_Pacific")
regional_ts_100(model.name = "MPI", region = "EQ_Pacific")
regional_ts_100(model.name = "UKESM", region = "EQ_Pacific")

regional_ts_100(model.name = "CESM", region = "low_lats_no_EQ_Pacific")
regional_ts_100(model.name = "CMCC", region = "low_lats_no_EQ_Pacific")
regional_ts_100(model.name = "EC-Earth", region ="low_lats_no_EQ_Pacific")
regional_ts_100(model.name = "GFDL", region = "low_lats_no_EQ_Pacific")
regional_ts_100(model.name = "IPSL", region = "low_lats_no_EQ_Pacific")
regional_ts_100(model.name = "MPI", region = "low_lats_no_EQ_Pacific")
regional_ts_100(model.name = "UKESM", region = "low_lats_no_EQ_Pacific")


```


3. Calculate regional POC flux time series at MLDmax, PCD, and 1000m
```{r}

setwd("~/senior_thesis/")
source('libraries.R')
setwd("~/regional_time_series_analysis/code/")
source('calc_regional_time_series_expc.R')
source('calc_regional_time_series_expc_UKESM.R')
models = c("CESM","CM4","CMCC", "EC-Earth", "GFDL", "IPSL", "MPI")
files = 1:6

# Southern Ocean South of 60 degrees ----------

lapply(models,regional_ts_expc, region = "SO_60", DH = "MLDmax")
lapply(models,regional_ts_expc, region = "SO_60", DH = 1000)
lapply(models,regional_ts_expc, region = "SO_60", DH = "PCD")

#UKESM calculate
lapply(files, regional_ts_expc_UKESM, region = "SO_60", DH = "MLDmax")
lapply(files, regional_ts_expc_UKESM, region = "SO_60", DH = "PCD")
lapply(files, regional_ts_expc_UKESM, region = "SO_60", DH = 1000)
#UKESM combine
DHs = c("MLDmax", "PCD", 1000)
lapply(DHs, combine_regional_ts_UKESM, region = "SO_60")


# Southern Ocean South of 50 Degrees ---------------

lapply(models,regional_ts_expc, region = "SO_50", DH = "MLDmax")
lapply(models,regional_ts_expc, region = "SO_50", DH = 1000)
lapply(models,regional_ts_expc, region = "SO_50", DH = "PCD")

#UKESM calculate
lapply(files, regional_ts_expc_UKESM, region = "SO_50", DH = "MLDmax")
lapply(files, regional_ts_expc_UKESM, region = "SO_50", DH = "PCD")
lapply(files, regional_ts_expc_UKESM, region = "SO_50", DH = 1000)
#UKESM combine
DHs = c("MLDmax", "PCD", 1000)
lapply(DHs, combine_regional_ts_UKESM, region = "SO_50")


# Low latitudes 30S-30N --------------

#takes 50min per model

lapply(models,regional_ts_expc, region = "30_low_lats", DH = "MLDmax")
lapply(models,regional_ts_expc, region = "30_low_lats", DH = 1000)
lapply(models,regional_ts_expc, region = "30_low_lats", DH = "PCD")

#UKESM calculate
lapply(files, regional_ts_expc_UKESM, region = "30_low_lats", DH = "MLDmax")
lapply(files, regional_ts_expc_UKESM, region = "30_low_lats", DH = "PCD")
lapply(files, regional_ts_expc_UKESM, region = "30_low_lats", DH = 1000)
#UKESM combine
DHs = c("MLDmax", "PCD", 1000)
lapply(DHs, combine_regional_ts_UKESM, region = "30_low_lats")


# Low latitudes 15S-15N --------------

#takes 20 minutes per model

lapply(models,regional_ts_expc, region = "15_low_lats", DH = "MLDmax")
lapply(models,regional_ts_expc, region = "15_low_lats", DH = 1000)
lapply(models,regional_ts_expc, region = "15_low_lats", DH = "PCD")

#UKESM calculate
lapply(files, regional_ts_expc_UKESM, region = "15_low_lats", DH = "MLDmax")
lapply(files, regional_ts_expc_UKESM, region = "15_low_lats", DH = "PCD")
lapply(files, regional_ts_expc_UKESM, region = "15_low_lats", DH = 1000)
#UKESM combine
DHs = c("MLDmax", "PCD", 1000)
lapply(DHs, combine_regional_ts_UKESM, region = "15_low_lats")


# Equatorial Pacific (15S to 15N, 160E to 75W)  --------------

#takes 10 minutes per model

lapply(models,regional_ts_expc, region = "EQ_Pacific", DH = "MLDmax")
lapply(models,regional_ts_expc, region = "EQ_Pacific", DH = 1000)
lapply(models,regional_ts_expc, region = "EQ_Pacific", DH = "PCD")

#UKESM calculate
lapply(files, regional_ts_expc_UKESM, region = "EQ_Pacific", DH = "MLDmax")
lapply(files, regional_ts_expc_UKESM, region = "EQ_Pacific", DH = "PCD")
lapply(files, regional_ts_expc_UKESM, region = "EQ_Pacific", DH = 1000)
#UKESM combine
DHs = c("MLDmax", "PCD", 1000)
lapply(DHs, combine_regional_ts_UKESM, region = "EQ_Pacific")

# Low Latitudes without Equatorial Pacific (30S to 30N without 15S to 15N, 160E to 75W)  --------------

#takes 50 minutes per model

lapply(models,regional_ts_expc, region = "low_lats_no_EQ_Pacific", DH = "MLDmax")
lapply(models,regional_ts_expc, region = "low_lats_no_EQ_Pacific", DH = 1000)
lapply(models,regional_ts_expc, region = "low_lats_no_EQ_Pacific", DH = "PCD")

#UKESM calculate
lapply(files, regional_ts_expc_UKESM, region = "low_lats_no_EQ_Pacific", DH = "MLDmax")
lapply(files, regional_ts_expc_UKESM, region = "low_lats_no_EQ_Pacific", DH = "PCD")
lapply(files, regional_ts_expc_UKESM, region = "low_lats_no_EQ_Pacific", DH = 1000)
#UKESM combine
DHs = c("MLDmax", "PCD", 1000)
lapply(DHs, combine_regional_ts_UKESM, region = "low_lats_no_EQ_Pacific")

# North Atlantic (40N to 65N, 70W to 0W)  --------------

#takes 5 minute per model

lapply(models,regional_ts_expc, region = "North_Atlantic", DH = "MLDmax")
lapply(models,regional_ts_expc, region = "North_Atlantic", DH = 1000)
lapply(models,regional_ts_expc, region = "North_Atlantic", DH = "PCD")

#UKESM calculate
lapply(files, regional_ts_expc_UKESM, region = "North_Atlantic", DH = "MLDmax")
lapply(files, regional_ts_expc_UKESM, region = "North_Atlantic", DH = "PCD")
lapply(files, regional_ts_expc_UKESM, region = "North_Atlantic", DH = 1000)
#UKESM combine
DHs = c("MLDmax", "PCD", 1000)
lapply(DHs, combine_regional_ts_UKESM, region = "North_Atlantic")


```


4. Calculate POC flux at the EZ depth
```{r}

setwd("~/senior_thesis/")
source('libraries.R')
setwd("~/regional_time_series_analysis/code/")
source('calc_regional_time_series_expc_ez.R')
source('calc_regional_time_series_expc_UKESM.R')
models = c("CESM","CMCC", "EC-Earth", "GFDL", "IPSL", "MPI")
files = 1:6

regions = c("SO_50", "SO_60", "30_low_lats", "15_low_lats","EQ_Pacific", "low_lats_no_EQ_Pacific", "North_Atlantic")

lapply(regions, regional_ts_expc_ez, model.name = "CM4")

lapply(models,regional_ts_expc_ez, region = "SO_50")
lapply(models,regional_ts_expc_ez, region = "SO_60")
lapply(models,regional_ts_expc_ez, region = "30_low_lats")
lapply(models,regional_ts_expc_ez, region = "15_low_lats")
lapply(models,regional_ts_expc_ez, region = "EQ_Pacific")
lapply(models,regional_ts_expc_ez, region = "low_lats_no_EQ_Pacific")
lapply(models,regional_ts_expc_ez, region = "North_Atlantic")

lapply(files, regional_ts_expc_UKESM, DH = "EZ_depth", region = "SO_50")
lapply(files, regional_ts_expc_UKESM, DH = "EZ_depth", region = "SO_60")
lapply(files, regional_ts_expc_UKESM, DH = "EZ_depth", region = "30_low_lats")
lapply(files, regional_ts_expc_UKESM, DH = "EZ_depth", region = "15_low_lats")
lapply(files, regional_ts_expc_UKESM, DH = "EZ_depth", region = "EQ_Pacific")
lapply(files, regional_ts_expc_UKESM, DH = "EZ_depth", region = "low_lats_no_EQ_Pacific")
lapply(files, regional_ts_expc_UKESM, DH = "EZ_depth", region = "North_Atlantic")

lapply(regions, combine_regional_ts_UKESM, DH = "EZ")

```


4. Calculate regionally integrated NPP 
```{r}

setwd("~/senior_thesis/")
source('libraries.R')
setwd("~/regional_time_series_analysis/code/")
source('calc_regional_time_series_npp.R')
source('calc_regional_time_series_npp_UKESM.R')
source('calc_regional_time_series_expc_UKESM.R') # for combining files
files = 1:5

#divide into lots of tmux sessions because this takes longer to run, CMCC takes even longer
models = c("CESM","CM4","EC-Earth") 
models =  c("GFDL","IPSL", "MPI")
          
lapply(models, regional_ts_npp, region = "SO_50")
regional_ts_npp(model.name = "CMCC", region = "SO_50")

lapply(models, regional_ts_npp, region = "SO_60")
regional_ts_npp(model.name = "CMCC", region = "SO_60")

lapply(models, regional_ts_npp, region = "30_low_lats")
regional_ts_npp(model.name = "CMCC", region = "30_low_lats")

lapply(models, regional_ts_npp, region = "15_low_lats")
regional_ts_npp(model.name = "CMCC", region = "15_low_lats")

lapply(models, regional_ts_npp, region = "North_Atlantic")

lapply(models, regional_ts_npp, region = "EQ_Pacific")

lapply(models, regional_ts_npp, region = "low_lats_no_EQ_Pacific")
regional_ts_npp(model.name = "CMCC", region = "low_lats_no_EQ_Pacific")

#UKESM
lapply(files, regional_ts_npp_UKESM, region = "SO_50")
lapply(files, regional_ts_npp_UKESM, region = "SO_60")
lapply(files, regional_ts_npp_UKESM, region = "30_low_lats")
lapply(files, regional_ts_npp_UKESM, region = "15_low_lats")
lapply(files, regional_ts_npp_UKESM, region = "North_Atlantic")
lapply(files, regional_ts_npp_UKESM, region = "EQ_Pacific")
lapply(files, regional_ts_npp_UKESM, region = "low_lats_no_EQ_Pacific")

#combine files
regions = c("SO_50", "SO_60", "30_low_lats", "15_low_lats","EQ_Pacific", "low_lats_no_EQ_Pacific", "North_Atlantic")
lapply(regions, combine_regional_ts_UKESM, DH = "NPP")

combine_regional_ts_UKESM( DH = "NPP", region = "EQ_Pacific")


```


6. Calculate regionally integrated TE and e-ratio
```{r}

setwd("~/regional_time_series_analysis/code/")
source('calc_regional_e_ratio_TE.R')

regions = c("SO_50", "SO_60", "30_low_lats", "15_low_lats","EQ_Pacific", "low_lats_no_EQ_Pacific", "North_Atlantic")

lapply(regions, regional_ts_TE, DH = "POC_100")
lapply(regions, regional_ts_TE, DH = "POC_PCD")
lapply(regions, regional_ts_TE, DH = "POC_EZ")
lapply(regions, regional_ts_TE, DH = "POC_MLDmax")

lapply(regions, regional_ts_e_ratio, DH = "POC_100")
lapply(regions, regional_ts_e_ratio, DH = "POC_PCD")
lapply(regions, regional_ts_e_ratio, DH = "POC_EZ")
lapply(regions, regional_ts_e_ratio, DH = "POC_MLDmax")
lapply(regions, regional_ts_e_ratio, DH = "POC_1000")

```


7. Plot regional time series - fluxes and NPP
```{r}

setwd("~/senior_thesis/")
source('libraries.R')
setwd("~/regional_time_series_analysis/code/")
source('plot_regional_time_series.R')

plot_regional_time_series(region = "SO_60", DH = "POC_100")
plot_regional_time_series(region = "SO_60", DH = "POC_MLDmax")
plot_regional_time_series(region = "SO_60", DH = "POC_PCD")
plot_regional_time_series(region = "SO_60", DH = "POC_1000")
plot_regional_time_series(region = "SO_60", DH = "POC_EZ")
plot_regional_time_series(region = "SO_60", DH = "NPP")

plot_regional_time_series(region = "SO_50", DH = "POC_100")
plot_regional_time_series(region = "SO_50", DH = "POC_MLDmax")
plot_regional_time_series(region = "SO_50", DH = "POC_PCD")
plot_regional_time_series(region = "SO_50", DH = "POC_1000")
plot_regional_time_series(region = "SO_50", DH = "POC_EZ")
plot_regional_time_series(region = "SO_50", DH = "NPP")

plot_regional_time_series(region = "30_low_lats", DH = "POC_100")
plot_regional_time_series(region = "30_low_lats", DH = "POC_MLDmax")
plot_regional_time_series(region = "30_low_lats", DH = "POC_PCD")
plot_regional_time_series(region = "30_low_lats", DH = "POC_EZ")
plot_regional_time_series(region = "30_low_lats", DH = "POC_1000")
plot_regional_time_series(region = "30_low_lats", DH = "NPP")

plot_regional_time_series(region = "15_low_lats", DH = "POC_100")
plot_regional_time_series(region = "15_low_lats", DH = "POC_MLDmax")
plot_regional_time_series(region = "15_low_lats", DH = "POC_PCD")
plot_regional_time_series(region = "15_low_lats", DH = "POC_EZ")
plot_regional_time_series(region = "15_low_lats", DH = "POC_1000")
plot_regional_time_series(region = "15_low_lats", DH = "NPP")

plot_regional_time_series(region = "EQ_Pacific", DH = "POC_100")
plot_regional_time_series(region = "EQ_Pacific", DH = "POC_MLDmax")
plot_regional_time_series(region = "EQ_Pacific", DH = "POC_PCD")
plot_regional_time_series(region = "EQ_Pacific", DH = "POC_EZ")
plot_regional_time_series(region = "EQ_Pacific", DH = "POC_1000")
plot_regional_time_series(region = "EQ_Pacific", DH = "NPP")

plot_regional_time_series(region = "low_lats_no_EQ_Pacific", DH = "POC_100")
plot_regional_time_series(region = "low_lats_no_EQ_Pacific", DH = "POC_MLDmax")
plot_regional_time_series(region = "low_lats_no_EQ_Pacific", DH = "POC_PCD")
plot_regional_time_series(region = "low_lats_no_EQ_Pacific", DH = "POC_EZ")
plot_regional_time_series(region = "low_lats_no_EQ_Pacific", DH = "POC_1000")
plot_regional_time_series(region = "low_lats_no_EQ_Pacific", DH = "NPP")

plot_regional_time_series(region = "North_Atlantic", DH = "POC_100")
plot_regional_time_series(region = "North_Atlantic", DH = "POC_MLDmax")
plot_regional_time_series(region = "North_Atlantic", DH = "POC_PCD")
plot_regional_time_series(region = "North_Atlantic", DH = "POC_EZ")
plot_regional_time_series(region = "North_Atlantic", DH = "POC_1000")
plot_regional_time_series(region = "North_Atlantic", DH = "NPP")

combine_figs(DH = 100)
combine_figs(DH = "MLDmax")
combine_figs(DH = 1000)
combine_figs(DH = "PCD")
combine_figs(DH = "EZ")
combine_figs(DH = "NPP")

combine_interrelations(DH = "POC_100", region = "SO_50")
combine_interrelations(DH = "POC_100", region = "SO_60")
combine_interrelations(DH = "POC_100", region = "low_lats_no_EQ_Pacific")
combine_interrelations(DH = "POC_100", region = "North_Atlantic")
combine_interrelations(DH = "POC_100", region = "EQ_Pacific")

```


8. Plot regional time series - e-ratio and TE
```{r}

setwd("~/senior_thesis/")
source('libraries.R')
setwd("~/regional_time_series_analysis/code/")
source('plot_regional_time_series_TE_e_ratio.R')

regions = c("SO_50", "SO_60", "30_low_lats", "15_low_lats","EQ_Pacific", "low_lats_no_EQ_Pacific", "North_Atlantic")


lapply(regions,plot_regional_ts_TE_e_ratio, DH = "POC_100")
lapply(regions,plot_regional_ts_TE_e_ratio, DH = "POC_PCD")
lapply(regions,plot_regional_ts_TE_e_ratio, DH = "POC_EZ")
lapply(regions,plot_regional_ts_TE_e_ratio, DH = "POC_MLDmax")
lapply(regions,plot_regional_ts_TE_e_ratio, DH = "POC_1000")

combine_regional_TE(DH = "POC_100")
combine_regional_TE(DH = "POC_PCD")
combine_regional_TE(DH = "POC_EZ")
combine_regional_TE(DH = "POC_MLDmax")

combine_regional_e_ratio(DH = "POC_100")
combine_regional_e_ratio(DH = "POC_PCD")
combine_regional_e_ratio(DH = "POC_EZ")
combine_regional_e_ratio(DH = "POC_MLDmax")
combine_regional_e_ratio(DH = "POC_1000")


```

