---
title: "CMIP6 POC Flux Comparisons Master Notebook - Spatial Analysis"
output: html_notebook
author: "Stevie Walker"
---

1. Install and load libraries 
```{r}

setwd("~/senior_thesis/")
source("libraries.R")

```

2. Regrid nc files
- GFDL and CM4 are already on a regular grid, so the files in ~/spatial_analysis/regridded_nc_files/GFDL_rg/ and ~/spatial_analysis/regridded_nc_files/CM4_rg/ are just the original combined nc files
```{r}
setwd("~/senior_thesis/")
source("libraries.R")
setwd("~/spatial_analysis/code/")
source('regrid_nc.R')

##epc100 ------------

regrid(model.name = "CESM", nc.file = "epc100_Omon_CESM2_historical_r1i1p1f1_gn_185001-201412.nc")
regrid(model.name = "CESM", nc.file = "epc100_Omon_CESM2_ssp585_r10i1p1f1_gn_201501-210012.nc")

regrid(model.name = "CMCC", nc.file = "epc100_Omon_CMCC-ESM2_historical_r1i1p1f1_gn_185001-201412.nc")
regrid(model.name = "CMCC", nc.file = "epc100_Omon_CMCC-ESM2_ssp585_r1i1p1f1_gn_201501-210012.nc")

regrid(model.name = "EC-Earth", nc.file = "epc100_Omon_EC-Earth3-CC_historical_r1i1p1f1_gn_185001-201412.nc")
regrid(model.name = "EC-Earth", nc.file = "epc100_Omon_EC-Earth3-CC_ssp585_r1i1p1f1_gn_201501-210012.nc")

regrid(model.name = "IPSL", nc.file = "epc100_Omon_IPSL-CM6A-LR_historical_r1i1p1f1_gn_185001-201412.nc")
regrid(model.name = "IPSL", nc.file = "epc100_Omon_IPSL-CM6A-LR_ssp585_r1i1p1f1_gn_201501-210012.nc") #didn't work

regrid(model.name = "MPI", nc.file = "epc100_Omon_MPI-ESM1-2-HR_historical_r1i1p1f1_gn_185001-201412.nc")
regrid(model.name = "MPI", nc.file = "epc100_Omon_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_201501-210012.nc")

regrid(model.name = "UKESM", nc.file = "epc100_Omon_UKESM1-0-LL_historical_r1i1p1f2_gn_185001-201412.nc")
regrid(model.name = "UKESM", nc.file = "epc100_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_201501-210012.nc")

##mlotst -----------

regrid(model.name = "CESM", nc.file = "mlotst_Omon_CESM2_historical_r10i1p1f1_gn_185001-201412.nc")
regrid(model.name = "CESM", nc.file = "mlotst_Omon_CESM2_ssp585_r10i1p1f1_gn_201501-210012.nc")

regrid(model.name = "CMCC", nc.file = "mlotst_Omon_CMCC-ESM2_historical_r1i1p1f1_gn_185001-201412.nc")
regrid(model.name = "CMCC", nc.file = "mlotst_Omon_CMCC-ESM2_ssp585_r1i1p1f1_gn_201501-210012.nc")

regrid(model.name = "EC-Earth", nc.file = "mlotst_Omon_EC-Earth3-CC_historical_r1i1p1f1_gn_185001-201412.nc")
regrid(model.name = "EC-Earth", nc.file = "mlotst_Omon_EC-Earth3-CC_ssp585_r1i1p1f1_gn_201501-210012.nc")

regrid(model.name = "IPSL", nc.file = "mlotst_Omon_IPSL-CM6A-LR_historical_r1i1p1f1_gn_185001-201412.nc")
regrid(model.name = "IPSL", nc.file = "mlotst_Omon_IPSL-CM6A-LR_ssp585_r1i1p1f1_gn_201501-210012.nc")

regrid(model.name = "MPI", nc.file = "mlotst_Omon_MPI-ESM1-2-HR_historical_r1i1p1f1_gn_185001-201412.nc")
regrid(model.name = "MPI", nc.file = "mlotst_Omon_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_201501-210012.nc")

regrid(model.name = "UKESM", nc.file = "mlotst_Omon_UKESM1-0-LL_historical_r1i1p1f2_gn_185001-201412.nc")
regrid(model.name = "UKESM", nc.file = "mlotst_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_201501-210012.nc")

##expc ------------

regrid(model.name = "CESM", nc.file = "expc_Oyr_CESM2_historical_r10i1p1f1_gn_1850-2014.nc")
regrid(model.name = "CESM", nc.file = "expc_Oyr_CESM2_ssp585_r10i1p1f1_gn_2015-2100.nc")

regrid(model.name = "CMCC", nc.file = "expc_Oyr_CMCC-ESM2_historical_r1i1p1f1_gn_1850-2014.nc")
regrid(model.name = "CMCC", nc.file = "expc_Oyr_CMCC-ESM2_ssp585_r1i1p1f1_gn_2015-2100.nc")

regrid(model.name = "EC-Earth", nc.file = "expc_Oyr_EC-Earth3-CC_historical_r1i1p1f1_gn_1850-2014.nc")
regrid(model.name = "EC-Earth", nc.file = "expc_Oyr_EC-Earth3-CC_ssp585_r1i1p1f1_gn_2015-2100.nc")

regrid(model.name = "IPSL", nc.file = "expc_Oyr_IPSL-CM6A-LR_historical_r1i1p1f1_gn_1850-2014.nc")
regrid(model.name = "IPSL", nc.file = "expc_Oyr_IPSL-CM6A-LR_ssp585_r1i1p1f1_gn_2015-2100.nc")

regrid(model.name = "MPI", nc.file = "expc_Oyr_MPI-ESM1-2-HR_historical_r1i1p1f1_gn_1850-2014.nc")
regrid(model.name = "MPI", nc.file = "expc_Oyr_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_2015-2100.nc")

#do an lapply here
expc_UKESM = list.files(path = "~/senior_thesis/combined_UKESM_files/", pattern = "expc")

lapply(expc_UKESM, regrid, model.name = "UKESM")

##pp -------------

regrid(model.name = "CESM", nc.file = "pp_Oyr_CESM2_historical_r10i1p1f1_gn_1850-2014.nc")
regrid(model.name = "CESM", nc.file = "pp_Oyr_CESM2_ssp585_r10i1p1f1_gn_2015-2100.nc")

regrid(model.name = "CMCC", nc.file = "pp_Omon_CMCC-ESM2_historical_r1i1p1f1_gn_185001-201412.nc")
regrid(model.name = "CMCC", nc.file = "pp_Omon_CMCC-ESM2_ssp585_r1i1p1f1_gn_201501-210012.nc")

#no historical EC-Earth data available
regrid(model.name = "EC-Earth", nc.file = "pp_Oyr_EC-Earth3-CC_ssp585_r1i1p1f1_gn_2015-2100.nc")

regrid(model.name = "IPSL", nc.file = "pp_Oyr_IPSL-CM6A-LR_historical_r1i1p1f1_gn_1850-2014.nc")
regrid(model.name = "IPSL", nc.file = "pp_Oyr_IPSL-CM6A-LR_ssp585_r1i1p1f1_gn_2015-2100.nc")

regrid(model.name = "MPI", nc.file = "pp_Oyr_MPI-ESM1-2-HR_historical_r1i1p1f1_gn_1850-2014.nc")
regrid(model.name = "MPI", nc.file = "pp_Oyr_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_2015-2100.nc")

#do an lapply here
pp_UKESM = list.files(path = "~/senior_thesis/combined_UKESM_files/", pattern = "pp")

lapply(pp_UKESM,regrid, model.name = "UKESM")

## areacello ----------

regrid(model.name = "CESM", nc.file = "areacello_Ofx_CESM2_historical_r10i1p1f1_gn.nc")
regrid(model.name = "CMCC", nc.file = "areacello_Ofx_CMCC-ESM2_historical_r1i1p1f1_gn.nc")
regrid(model.name = "EC-Earth", nc.file = "areacello_Ofx_EC-Earth3-CC_historical_r1i1p1f1_gn.nc")
regrid(model.name = "IPSL", nc.file = "areacello_Ofx_IPSL-CM6A-LR_ssp585_r1i1p1f1_gn.nc")
regrid(model.name = "MPI", nc.file = "areacello_Ofx_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn.nc")
regrid(model.name = "UKESM", nc.file = "areacello_Ofx_UKESM1-0-LL_piControl_r1i1p1f2_gn.nc")

```

3. Calculate and plot historical average, long-term average, and change in POC flux at 100m
```{r}

setwd("~/senior_thesis/")
source("libraries.R")
source("get_time.R")
setwd("~/spatial_analysis/code/")
source("rg_calc_epc100_avg.R")
source("rg_plot_POC_100.R")
source("calc_multimodel_avg.R")

options(max.print = 2000)

## CESM --------------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/CESM_rg/",
         file.name = 'epc100_Omon_CESM2_ssp585_r10i1p1f1_gn_201501-210012_rg.nc')

get_time(data.path = "~/spatial_analysis/regridded_nc_files/CESM_rg/",
         file.name = 'epc100_Omon_CESM2_historical_r1i1p1f1_gn_185001-201412_rg.nc')

calc_epc100_avg(model.name = "CESM")

## CM4 ------

#calculate using rg_calc_expc_avg since this model did not archive epc100 data


## CMCC -----------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/CMCC_rg/",
         file.name = 'epc100_Omon_CMCC-ESM2_ssp585_r1i1p1f1_gn_201501-210012_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/CMCC_rg/",
         file.name = 'epc100_Omon_CMCC-ESM2_historical_r1i1p1f1_gn_185001-201412_rg.nc')

calc_epc100_avg(model.name = "CMCC")

##EC-Earth ------------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/EC-Earth_rg/",
         file.name = 'epc100_Omon_EC-Earth3-CC_ssp585_r1i1p1f1_gn_201501-210012_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/EC-Earth_rg/",
         file.name = 'epc100_Omon_EC-Earth3-CC_historical_r1i1p1f1_gn_185001-201412_rg.nc')

calc_epc100_avg(model.name = "EC-Earth")

##GFDL --------------
get_time(data.path = "~/spatial_analysis/regridded_nc_files/GFDL_rg/",
         file.name = 'epc100_Omon_GFDL-ESM4_historical_r1i1p1f1_gr_185001-201412.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/GFDL_rg/",
         file.name = 'epc100_Omon_GFDL-ESM4_ssp585_r1i1p1f1_gr_201501-210012.nc')

calc_epc100_avg(model.name = "GFDL")

## IPSL ------------
get_time(data.path = "~/spatial_analysis/regridded_nc_files/IPSL_rg/",
         file.name = 'epc100_Omon_IPSL-CM6A-LR_historical_r1i1p1f1_gn_185001-201412_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/IPSL_rg/",
         file.name = 'epc100_Omon_IPSL-CM6A-LR_ssp585_r1i1p1f1_gn_201501-210012_rg.nc')

calc_epc100_avg(model.name = "IPSL")

## MPI --------------
get_time(data.path = "~/spatial_analysis/regridded_nc_files/MPI_rg/",
         file.name = 'epc100_Omon_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_201501-210012_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/MPI_rg/",
         file.name = 'epc100_Omon_MPI-ESM1-2-HR_historical_r1i1p1f1_gn_185001-201412_rg.nc')

calc_epc100_avg(model.name = "MPI")

## UKESM --------
get_time(data.path = "~/spatial_analysis/regridded_nc_files/UKESM_rg/",
         file.name = 'epc100_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_201501-210012_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/UKESM_rg/",
         file.name = 'epc100_Omon_UKESM1-0-LL_historical_r1i1p1f2_gn_185001-201412_rg.nc')

calc_epc100_avg(model.name = "UKESM")

#calculate multimodel average ---------

calc_multimodel_avg(variable = "POC_100", varname = "epc100")

#plot individual model maps -------

setwd("~/spatial_analysis/code/")
source("rg_plot_POC_100.R")

land <- ne_download(scale = 50, type = 'land', category = 'physical')
world <- ne_load(scale = 50, type = 'land', category = 'physical', returnclass = "sf")

models = c("CESM", "CM4", "CMCC", "EC-Earth", "GFDL", "IPSL", "MPI", "UKESM", "multimodel")

lapply(models, plot_POC_100)

```

4. Calculate historical average, long-term average, and change in maximum annual mixed layer depth
```{r}

setwd("~/senior_thesis/")
source("libraries.R")
source("get_time.R")
setwd("~/spatial_analysis/code/")
source("rg_calc_MLD_max.R")
source("rg_plot_MLD_max.R")

## CESM --------------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/CESM_rg/",
         file.name = 'mlotst_Omon_CESM2_ssp585_r10i1p1f1_gn_201501-210012_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/CESM_rg/",
         file.name = 'mlotst_Omon_CESM2_historical_r10i1p1f1_gn_185001-201412_rg.nc')

calc_MLD_max(model.name = "CESM")

## CM4 -----------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/CM4_rg/",
         file.name = 'mlotst_Omon_GFDL-CM4_historical_r1i1p1f1_gr_185001-201412.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/CM4_rg/",
         file.name = 'mlotst_Omon_GFDL-CM4_ssp585_r1i1p1f1_gr_201501-210012.nc')

calc_MLD_max(model.name = "CM4")

## CMCC -----------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/CMCC_rg/",
         file.name = 'mlotst_Omon_CMCC-ESM2_ssp585_r1i1p1f1_gn_201501-210012_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/CMCC_rg/",
         file.name = 'mlotst_Omon_CMCC-ESM2_historical_r1i1p1f1_gn_185001-201412_rg.nc')

calc_MLD_max(model.name = "CMCC")

##EC-Earth ------------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/EC-Earth_rg/",
         file.name = 'mlotst_Omon_EC-Earth3-CC_ssp585_r1i1p1f1_gn_201501-210012_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/EC-Earth_rg/",
         file.name = 'mlotst_Omon_EC-Earth3-CC_historical_r1i1p1f1_gn_185001-201412_rg.nc')

calc_MLD_max(model.name = "EC-Earth")

##GFDL --------------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/GFDL_rg/",
         file.name = 'mlotst_Omon_GFDL-ESM4_historical_r1i1p1f1_gr_185001-201412.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/GFDL_rg/",
         file.name = 'mlotst_Omon_GFDL-ESM4_ssp585_r1i1p1f1_gr_201501-210012.nc')

calc_MLD_max(model.name = "GFDL")

## IPSL -----------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/IPSL_rg/",
         file.name = 'mlotst_Omon_IPSL-CM6A-LR_historical_r1i1p1f1_gn_185001-201412_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/IPSL_rg/",
         file.name = 'mlotst_Omon_IPSL-CM6A-LR_ssp585_r1i1p1f1_gn_201501-210012_rg.nc')

calc_MLD_max(model.name = "IPSL")

## MPI --------------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/MPI_rg/",
         file.name = 'mlotst_Omon_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_201501-210012_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/MPI_rg/",
         file.name = 'mlotst_Omon_MPI-ESM1-2-HR_historical_r1i1p1f1_gn_185001-201412_rg.nc')

calc_MLD_max(model.name = "MPI")

## UKESM ------------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/UKESM_rg/",
         file.name = 'mlotst_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_201501-210012_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/UKESM_rg/",
         file.name = 'mlotst_Omon_UKESM1-0-LL_historical_r1i1p1f2_gn_185001-201412_rg.nc')

calc_MLD_max(model.name = "UKESM")

#calculate multimodel average ---------

calc_multimodel_avg(variable = "MLD_max", varname = "mlotst")

#plotting --------

setwd("~/spatial_analysis/code/")
source("rg_plot_MLD_max.R")

land <- ne_download(scale = 50, type = 'land', category = 'physical')
world <- ne_load(scale = 50, type = 'land', category = 'physical', returnclass = "sf")

models = c("CESM", "CM4", "CMCC", "EC-Earth", "GFDL", "IPSL", "MPI", "UKESM", "multimodel")

lapply(models, plot_MLD_max)

```

5. Calculate historical average and long-term average EZ Depth
``` {r}
setwd("~/senior_thesis/")
source("libraries.R")
setwd("~/spatial_analysis/code/")
source("rg_calc_ez_depth.R")
source("calc_model_agreement.R")
source("calc_multimodel_avg.R")
source("rg_plot_ez_depth.R")

## CESM --------------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/CESM_rg/",
         file.name = 'pp_Oyr_CESM2_historical_r10i1p1f1_gn_1850-2014_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/CESM_rg/",
         file.name = 'pp_Oyr_CESM2_ssp585_r10i1p1f1_gn_2015-2100_rg.nc')

calc_ez_depth(model.name = "CESM", ez.metric = 1)
calc_ez_depth(model.name = "CESM", ez.metric = 5)

## CM4 ------------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/CM4_rg/",
         file.name = 'pp_Oyr_GFDL-CM4_historical_r1i1p1f1_gr_1850-2014.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/CM4_rg/",
         file.name = 'pp_Oyr_GFDL-CM4_ssp585_r1i1p1f1_gr_2015-2100.nc')

calc_ez_depth(model.name = "CM4", ez.metric = 1)
calc_ez_depth(model.name = "CM4", ez.metric = 5)
calc_ez_depth(model.name = "CM4", ez.metric = 10)

## CMCC -----------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/CMCC_rg/",
         file.name = 'pp_Omon_CMCC-ESM2_historical_r1i1p1f1_gn_185001-201412_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/CMCC_rg/",
         file.name = 'pp_Omon_CMCC-ESM2_ssp585_r1i1p1f1_gn_201501-210012_rg.nc')

calc_ez_depth(model.name = "CMCC", ez.metric = 1)
calc_ez_depth(model.name = "CMCC", ez.metric = 5)

##EC-Earth ------------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/EC-Earth_rg/",
         file.name = 'pp_Oyr_EC-Earth3-CC_ssp585_r1i1p1f1_gn_2015-2100_rg.nc')
#missing historical data

calc_ez_depth(model.name = "EC-Earth", ez.metric = 1)
calc_ez_depth(model.name = "EC-Earth", ez.metric = 5)

##GFDL --------------
get_time(data.path = "~/spatial_analysis/regridded_nc_files/GFDL_rg/",
         file.name = 'pp_Oyr_GFDL-ESM4_historical_r1i1p1f1_gr_1850-2014.nc')

get_time(data.path = "~/spatial_analysis/regridded_nc_files/GFDL_rg/",
         file.name = 'pp_Oyr_GFDL-ESM4_ssp585_r1i1p1f1_gr_2015-2100.nc')

calc_ez_depth(model.name = "GFDL", ez.metric = 1)
calc_ez_depth(model.name = "GFDL", ez.metric = 5)

## IPSL -----------
get_time(data.path = "~/spatial_analysis/regridded_nc_files/IPSL_rg/",
         file.name = 'pp_Oyr_IPSL-CM6A-LR_historical_r1i1p1f1_gn_1850-2014_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/IPSL_rg/",
         file.name = 'pp_Oyr_IPSL-CM6A-LR_ssp585_r1i1p1f1_gn_2015-2100_rg.nc')

calc_ez_depth(model.name = "IPSL", ez.metric = 1)
calc_ez_depth(model.name = "IPSL", ez.metric = 5)

## MPI --------------
get_time(data.path = "~/spatial_analysis/regridded_nc_files/MPI_rg/",
         file.name = 'pp_Oyr_MPI-ESM1-2-HR_historical_r1i1p1f1_gn_1850-2014_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/MPI_rg/",
         file.name = 'pp_Oyr_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_2015-2099_rg.nc')

calc_ez_depth(model.name = "MPI", ez.metric = 1)
calc_ez_depth(model.name = "MPI", ez.metric = 5)

## UKESM ------------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/UKESM_rg/",
         file.name = 'pp_Omon_UKESM1-0-LL_historical_r1i1p1f2_gn_185001-189912_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/UKESM_rg/",
         file.name = 'pp_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_201501-210012_rg.nc')

calc_ez_depth(model.name = "UKESM", ez.metric = 1)
calc_ez_depth(model.name = "UKESM", ez.metric = 5)

calc_multimodel_avg(variable = "EZ_depth", varname = "pp")
calc_multimodel_avg_5(variable = "EZ_depth", varname = "pp")

land <- ne_download(scale = 50, type = 'land', category = 'physical')
world <- ne_load(scale = 50, type = 'land', returnclass = "sf")

plot_EZ_depth("CESM", 1)
plot_EZ_depth("CM4", 1)
plot_EZ_depth("CM4", 10)
plot_EZ_depth("CMCC", 1)
plot_EZ_depth("EC-Earth", 1)
plot_EZ_depth("IPSL", 1)
plot_EZ_depth("GFDL", 1)
plot_EZ_depth("MPI", 1)
plot_EZ_depth("UKESM", 1)
plot_EZ_depth("multimodel", 1)

plot_EZ_depth("CESM", 5)
plot_EZ_depth("CM4", 5)
plot_EZ_depth("CMCC", 5)
plot_EZ_depth("EC-Earth", 5)
plot_EZ_depth("IPSL", 5)
plot_EZ_depth("GFDL", 5)
plot_EZ_depth("MPI", 5)
plot_EZ_depth("UKESM", 5)
plot_EZ_depth("multimodel", 5)

```

6. Calculate particle compensation depth
```{r}

setwd("~/senior_thesis/")
source("libraries.R")
setwd("~/spatial_analysis/code/")
source("rg_calc_PCD.R")
source("rg_plot_PCD.R") #this function also calculates PCD change
source("calc_multimodel_avg.R")

calc_PCD("CESM")
calc_PCD("CMCC")
calc_PCD("CM4")
calc_PCD("EC-Earth")
calc_PCD("GFDL")
calc_PCD("IPSL")
calc_PCD("MPI")
calc_PCD("UKESM")

calc_multimodel_avg(variable = "PCD", varname = "depth")

models = c("CESM", "CM4", "CMCC", "EC-Earth", "GFDL", "IPSL", "MPI", "UKESM", "multimodel")

lapply(models, plot_PCD)

```

6. Calculate historical average, long-term average, and change in POC flux at 1000m, MLDmax, EZ Depth, and PCD
```{r}
setwd("~/senior_thesis/")
source("libraries.R")
setwd("~/spatial_analysis/code/")
source("rg_calc_expc_avg.R")
source("calc_multimodel_avg.R")

## CESM --------------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/CESM_rg/",
         file.name = 'expc_Oyr_CESM2_historical_r10i1p1f1_gn_1850-2014_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/CESM_rg/",
         file.name = 'expc_Oyr_CESM2_ssp585_r10i1p1f1_gn_2015-2100_rg.nc')

calc_expc(model.name = "CESM", depth = 1000, ez.metric = NA)
calc_expc(model.name = "CESM", depth = "MLD_max", ez.metric = NA)
calc_expc(model.name = "CESM", depth = "EZ_depth", ez.metric = 1)
calc_expc(model.name = "CESM", depth = "EZ_depth", ez.metric = 5)
calc_expc(model.name = "CESM", depth = "PCD", ez.metric = NA)

## CM4 --------------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/CM4_rg/",
         file.name = 'expc_Oyr_GFDL-CM4_historical_r1i1p1f1_gr_1850-2014.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/CM4_rg/",
         file.name = 'expc_Oyr_GFDL-CM4_ssp585_r1i1p1f1_gr_2015-2100.nc')ß

calc_expc(model.name = "CM4", depth = 100, ez.metric = NA)
calc_expc(model.name = "CM4", depth = 1000, ez.metric = NA)
calc_expc(model.name = "CM4", depth = "MLD_max", ez.metric = NA)
calc_expc(model.name = "CM4", depth = "EZ_depth", ez.metric = 1)
calc_expc(model.name = "CM4", depth = "EZ_depth", ez.metric = 5)
calc_expc(model.name = "CM4", depth = "EZ_depth", ez.metric = 10)
calc_expc(model.name = "CM4", depth = "PCD", ez.metric = NA)

## CMCC -----------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/CMCC_rg/",
         file.name = 'expc_Oyr_CMCC-ESM2_historical_r1i1p1f1_gn_1850-2014_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/CMCC_rg/",
         file.name = 'expc_Oyr_CMCC-ESM2_ssp585_r1i1p1f1_gn_2015-2100_rg.nc')

calc_expc(model.name = "CMCC", depth = 1000, ez.metric = NA)
calc_expc(model.name = "CMCC", depth = "MLD_max", ez.metric = NA)
calc_expc(model.name = "CMCC", depth = "EZ_depth", ez.metric = 1)
#calc_expc(model.name = "CMCC", depth = "EZ_depth", ez.metric = 5)
calc_expc(model.name = "CMCC", depth = "PCD", ez.metric = NA)

##EC-Earth ------------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/EC-Earth_rg/",
         file.name = 'expc_Oyr_EC-Earth3-CC_historical_r1i1p1f1_gn_1850-2014_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/EC-Earth_rg/",
         file.name = 'expc_Oyr_EC-Earth3-CC_ssp585_r1i1p1f1_gn_2015-2100_rg.nc')

calc_expc(model.name = "EC-Earth", depth = 1000, ez.metric = NA)
calc_expc(model.name = "EC-Earth", depth = "MLD_max", ez.metric = NA)
calc_expc(model.name = "EC-Earth", depth = "EZ_depth", ez.metric = 1)
calc_expc(model.name = "EC-Earth", depth = "EZ_depth", ez.metric = 5)
calc_expc(model.name = "EC-Earth", depth = "PCD", ez.metric = NA)

##GFDL --------------
get_time(data.path = "~/spatial_analysis/regridded_nc_files/GFDL_rg/",
         file.name = 'expc_Oyr_GFDL-ESM4_historical_r1i1p1f1_gr_1850-2014.nc')

get_time(data.path = "~/spatial_analysis/regridded_nc_files/GFDL_rg/",
         file.name = 'expc_Oyr_GFDL-ESM4_ssp585_r1i1p1f1_gr_2015-2100.nc')

calc_expc(model.name = "GFDL", depth = 1000, ez.metric = NA)
calc_expc(model.name = "GFDL", depth = "MLD_max", ez.metric = NA)
calc_expc(model.name = "GFDL", depth = "EZ_depth", ez.metric = 1)
calc_expc(model.name = "GFDL", depth = "EZ_depth", ez.metric = 5)
calc_expc(model.name = "GFDL", depth = "PCD", ez.metric = NA)

## IPSL -----------
get_time(data.path = "~/spatial_analysis/regridded_nc_files/IPSL_rg/",
         file.name = 'expc_Oyr_IPSL-CM6A-LR_historical_r1i1p1f1_gn_1850-2014_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/IPSL_rg/",
         file.name = 'expc_Oyr_IPSL-CM6A-LR_ssp585_r1i1p1f1_gn_2015-2100_rg.nc')

calc_expc(model.name = "IPSL", depth = 1000, ez.metric = NA)
calc_expc(model.name = "IPSL", depth = "MLD_max", ez.metric = NA)
calc_expc(model.name = "IPSL", depth = "EZ_depth", ez.metric = 1)
calc_expc(model.name = "IPSL", depth = "EZ_depth", ez.metric = 5)
calc_expc(model.name = "IPSL", depth = "PCD", ez.metric = NA)

## MPI --------------
get_time(data.path = "~/spatial_analysis/regridded_nc_files/MPI_rg/",
         file.name = 'expc_Oyr_MPI-ESM1-2-HR_historical_r1i1p1f1_gn_1850-2014_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/MPI_rg/",
         file.name = 'expc_Oyr_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_2015-2100_rg.nc')

calc_expc(model.name = "MPI", depth = 1000, ez.metric = NA)
calc_expc(model.name = "MPI", depth = "MLD_max", ez.metric = NA)
calc_expc(model.name = "MPI", depth = "EZ_depth", ez.metric = 1)
calc_expc(model.name = "MPI", depth = "EZ_depth", ez.metric = 5)
calc_expc(model.name = "MPI", depth = "PCD", ez.metric = NA)

## UKESM ------------

get_time(data.path = "~/spatial_analysis/regridded_nc_files/UKESM_rg/",
         file.name = 'expc_Omon_UKESM1-0-LL_historical_r1i1p1f2_gn_185001-189912_rg.nc')
get_time(data.path = "~/spatial_analysis/regridded_nc_files/UKESM_rg/",
         file.name = 'expc_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_205001-210012_rg.nc')

calc_expc(model.name = "UKESM", depth = 1000, ez.metric = NA)
calc_expc(model.name = "UKESM", depth = "MLD_max", ez.metric = NA)
calc_expc(model.name = "UKESM", depth = "EZ_depth", ez.metric = 1)
calc_expc(model.name = "UKESM", depth = "EZ_depth", ez.metric = 5)
calc_expc(model.name = "UKESM", depth = "PCD", ez.metric = NA)

# calculate multimodel average ---------

calc_multimodel_avg(variable = "POC_1000", varname = "expc")
calc_multimodel_avg(variable = "POC_MLD_max", varname = "expc")
calc_multimodel_avg(variable = "POC_EZ_depth", varname = "expc")
calc_multimodel_avg(variable = "POC_PCD", varname = "expc")
calc_multimodel_avg_5(variable = "POC_EZ_depth", varname = "expc")

# plotting -------

setwd("~/senior_thesis/")
source("libraries.R")
setwd("~/spatial_analysis/code/")
source("rg_plot_expc.R")
source("rg_plot_POC_ez_depth.R")

land <- ne_download(scale = 50, type = 'land', category = 'physical')
world <- ne_load(scale = 50, type = 'land', category = 'physical', returnclass = "sf")

models = c("CESM", "CM4", "CMCC", "EC-Earth", "GFDL", "IPSL", "MPI", "UKESM", "multimodel")

lapply(models , plot_expc, variable = "1000")
lapply(models , plot_expc, variable = "PCD")
lapply(models , plot_expc, variable = "MLD_max")

lapply(models, plot_POC_EZ_depth, ez.metric = 1)
lapply(models, plot_POC_EZ_depth, ez.metric = 5)
plot_POC_EZ_depth("CM4", ez.metric = 10)

```


7. EZ depth metric sensitivity test - comparing 1% and 5% NPP max definitions 
```{r}
setwd("~/senior_thesis/")
source("libraries.R")
setwd("~/spatial_analysis/code/")
source("rg_plot_ez_depth.R")
source("rg_plot_POC_ez_depth.R")
source("calc_multimodel_avg.R")
source("rg_calc_ez_depth_sensitivity.R")

calc_ez_depth_diff("CESM")
calc_ez_depth_diff("CMCC")
calc_ez_depth_diff("EC-Earth")
calc_ez_depth_diff("GFDL")
calc_ez_depth_diff("IPSL")
calc_ez_depth_diff("MPI")
calc_ez_depth_diff("UKESM")

calc_multimodel_avg(variable = "EZ_depth_sensitivity", varname = "pp")
calc_multimodel_avg(variable = "POC_EZ_depth_sensitivity", varname = "pp")

models = c("CESM", "CM4", "CMCC", "EC-Earth", "GFDL", "IPSL", "MPI", "UKESM", "multimodel")

lapply(models, plot_metric_diff_EZ)
lapply(models, plot_metric_diff_POC_EZ)

```

8. Calculate water-column integrated historical, long-term, and change in NPP
- no need to double check the timesteps because I already did in step 5
```{r}
setwd("~/senior_thesis/")
source("libraries.R")
setwd("~/spatial_analysis/code/")
source("rg_calc_NPP.R")
source("calc_multimodel_avg.R")

calc_npp_avg("CESM")
calc_npp_avg("CM4")
calc_npp_avg("CMCC")
calc_npp_avg("EC-Earth")
calc_npp_avg("GFDL")
calc_npp_avg("IPSL")
calc_npp_avg("MPI")
calc_npp_avg("UKESM")

calc_multimodel_avg("NPP")

#plotting -------

setwd("~/spatial_analysis/code/")
source("rg_plot_NPP.R")

land <- ne_download(scale = 50, type = 'land', category = 'physical')
world <- ne_load(scale = 50, type = 'land', category = 'physical', returnclass = "sf")

models = c("CESM", "CM4", "CMCC", "EC-Earth", "GFDL", "IPSL", "MPI", "UKESM", "multimodel")
lapply(models, plot_NPP)

```

9. Calculate historical, long-term, and change in transfer efficiency from each depth horizon to 1000m
```{r}
setwd("~/senior_thesis/")
source('libraries.R')
setwd("~/spatial_analysis/code/")
source("rg_calc_TE_e-ratio.R")
source("calc_multimodel_avg.R")
source("rg_plot_TE.R")

models = c("CESM", "CM4", "CMCC", "EC-Earth", "GFDL", "IPSL", "MPI", "UKESM")

lapply(models, calc_TE, DH = "100")
lapply(models, calc_TE, DH = "MLD_max")
lapply(models, calc_TE, DH = "EZ_depth")
lapply(models, calc_TE, DH = "PCD")

calc_multimodel_avg_2(DH=100,variable = "TE")
calc_multimodel_avg_2(DH= "MLD_max", variable = "TE")
calc_multimodel_avg_2(DH= "EZ_depth", variable = "TE")
calc_multimodel_avg_2(DH= "PCD", variable = "TE")

calc_multimodel_avg_absolute(DH=100,variable = "TE")
calc_multimodel_avg_absolute(DH= "MLD_max", variable = "TE")
calc_multimodel_avg_absolute(DH= "EZ_depth", variable = "TE")
calc_multimodel_avg_absolute(DH= "PCD", variable = "TE")

#plotting TE -----------

land <- ne_download(scale = 50, type = 'land', category = 'physical')
world <- ne_load(scale = 50, type = 'land', category = 'physical', returnclass = "sf")

models = c("CESM", "CM4", "CMCC", "EC-Earth", "GFDL", "IPSL", "MPI", "UKESM", "multimodel")

lapply(models, plot_TE_by_model, variable = "POC_100", type = "percent")
lapply(models, plot_TE_by_model, variable = "POC_100", type = "absolute")
lapply(models, plot_TE_by_model, variable = "POC_MLD_max", type = "percent")
lapply(models, plot_TE_by_model, variable = "POC_MLD_max", type = "absolute")
lapply(models, plot_TE_by_model, variable = "POC_EZ_depth", type = "percent")
lapply(models, plot_TE_by_model, variable = "POC_EZ_depth", type = "absolute")
lapply(models, plot_TE_by_model, variable = "POC_PCD", type = "percent")
lapply(models, plot_TE_by_model, variable = "POC_PCD", type = "absolute")


```


10. Calculate historical, long-term, and change in e-ratio at each depth horizon
```{r}

setwd("~/spatial_analysis/code/")
source("rg_calc_TE_e-ratio.R")
source("rg_plot_e_ratio.R")
source("calc_multimodel_avg.R")

#calculate e-ratio --------

models = c("CESM", "CM4", "CMCC", "EC-Earth", "GFDL", "IPSL", "MPI", "UKESM")

lapply(models, calc_e_ratio, DH = "PCD")
lapply(models, calc_e_ratio, DH = "100")
lapply(models, calc_e_ratio, DH = "MLD_max")
lapply(models, calc_e_ratio, DH = "EZ_depth")
lapply(models, calc_e_ratio, DH = "1000")

calc_multimodel_avg_2(DH=100,variable = "e_ratio")
calc_multimodel_avg_2(DH= "MLD_max", variable = "e_ratio")
calc_multimodel_avg_2(DH= "EZ_depth", variable = "e_ratio")
calc_multimodel_avg_2(DH="PCD",variable = "e_ratio")
calc_multimodel_avg_2(DH=1000,variable = "e_ratio")

#plotting --------

#download/load land shapefile
land <- ne_download(scale = 50, type = 'land', category = 'physical')
world <- ne_load(scale = 50, type = 'land', category = 'physical', returnclass = "sf")

models = c("CESM", "CM4", "CMCC", "EC-Earth", "GFDL", "IPSL", "MPI", "UKESM", "multimodel")

lapply(models, plot_e_ratio, DH = "100")
lapply(models, plot_e_ratio, DH = "EZ_depth")
lapply(models, plot_e_ratio, DH = "MLD_max")
lapply(models, plot_e_ratio, DH = "PCD")
lapply(models, plot_e_ratio, DH = "1000")

```

11. Calculate model agreement on the sign of variable change
```{r}

setwd("~/spatial_analysis/code/")
source("calc_model_agreement.R")

calc_model_agreement(variable = "POC_100")
calc_model_agreement(variable = "POC_EZ_depth")
calc_model_agreement(variable = "POC_MLD_max")
calc_model_agreement(variable = "POC_1000")
calc_model_agreement(variable = "POC_PCD")
calc_model_agreement(variable = "MLD_max")
calc_model_agreement(variable = "NPP")
calc_model_agreement(variable = "PCD")
calc_model_agreement(variable = "EZ_depth")
calc_model_agreement(variable = "all_DH")
calc_model_agreement(variable = "POC_100_EZ_depth")
calc_model_agreement(variable = "POC_100_MLD_max")
calc_model_agreement(variable = "POC_100_1000")
calc_model_agreement(variable = "POC_100_PCD")
calc_model_agreement(variable = "POC_shallow_DHs")
calc_model_agreement(variable = "e_ratio") #100 m
calc_model_agreement(variable = "TE") #100 m

```


12. Assess differences in POC flux between 100m and EZ depth, PCD, and MLDmax 
```{r}

setwd("~/spatial_analysis/code/")
source("DH_differences_assessment.R")

#download/load land shapefile
land <- ne_download(scale = 50, type = 'land', category = 'physical')
world <- ne_load(scale = 50, type = 'land', category = 'physical', returnclass = "sf")

models = c("CESM", "CM4", "CMCC", "GFDL", "IPSL", "MPI", "UKESM", "multimodel")
lapply(models, plot_POC_DH_diff, DH = "EZ_depth")
models = c("CESM", "CM4", "CMCC", "EC-Earth", "GFDL", "IPSL", "MPI", "UKESM", "multimodel")
lapply(models, plot_POC_DH_diff, DH = "MLDmax")
lapply(models, plot_POC_DH_diff, DH = "PCD")

plot_POC_DH_diff("multimodel", "EZ_depth")
plot_POC_DH_diff("multimodel", "MLDmax")
plot_POC_DH_diff("multimodel", "PCD")

setwd("~/spatial_analysis/figures/POC_DH_differences/")
A <- readPNG('multimodel_POC_EZ_depth_POC_100_differences.png')
B <- readPNG('multimodel_POC_PCD_POC_100_differences.png')
C <- readPNG('multimodel_POC_MLDmax_POC_100_differences.png')

grid.combine <- grid.arrange(rasterGrob(A),rasterGrob(B),rasterGrob(C), ncol=1, nrow=3)

ggsave(paste("multimodel_POC_DH_differences.png",sep=""), plot = grid.combine, path = "~/spatial_analysis/figures/POC_DH_differences/", width = 30, height = 20, units = "cm", dpi = 400)

```
