---
title: "Time Series Analysis Notebook"
author: Stevie Walker
output: html_notebook
description: calculating and plotting globally integrated time series change in POC flux at each depth horizon, NPP, stratification, TE, e-ratio

---

1. Calculating globally integrated POC flux at 100m for every year (1850-2100)
```{r}

setwd('~/senior_thesis/')
source('libraries.R')
source('get_time.R')
setwd('~/time_series_analysis/code/')
source('calc_time_series_epc100.R')
source('calc_time_series_expc.R')

## CESM ---------------

get_time(data.path = "~/senior_thesis/combined_CESM_files/",
         file.name = 'epc100_Omon_CESM2_historical_r10i1p1f1_gn_185001-201412.nc')
get_time(data.path = "~/senior_thesis/combined_CESM_files/",
         file.name = 'epc100_Omon_CESM2_ssp585_r10i1p1f1_gn_201501-210012.nc')

time_series_100(model.name = "CESM")

## CM4 --------------

get_time(data.path = "~/senior_thesis/combined_CM4_files/",
         file.name = 'expc_Oyr_GFDL-CM4_historical_r1i1p1f1_gr_1850-2014.nc')
get_time(data.path = "~/senior_thesis/combined_CM4_files/",
         file.name = 'expc_Oyr_GFDL-CM4_ssp585_r1i1p1f1_gr_2015-2100.nc')

#use time series expc function because there is no epc100 data for this model, so you have to interpolate to get 100m POC flux
time_series_expc(model.name = "CM4",
                 lon.length = 1:360,
                 lat.length = 1:180,
                 DH = 100)

## CMCC ---------------

get_time(data.path = "~/senior_thesis/combined_CMCC_files/",
         file.name = 'epc100_Omon_CMCC-ESM2_historical_r1i1p1f1_gn_185001-201412.nc')
get_time(data.path = "~/senior_thesis/combined_CMCC_files/",
         file.name = 'epc100_Omon_CMCC-ESM2_ssp585_r1i1p1f1_gn_201501-210012.nc')

time_series_100(model.name = "CMCC")

## EC-Earth ------------

get_time(data.path = "~/senior_thesis/combined_EC-Earth_files/",
         file.name = 'epc100_Omon_EC-Earth3-CC_historical_r1i1p1f1_gn_185001-201412.nc')
get_time(data.path = "~/senior_thesis/combined_EC-Earth_files/",
         file.name = 'epc100_Omon_EC-Earth3-CC_ssp585_r1i1p1f1_gn_201501-210012.nc')

time_series_100(model.name = "EC-Earth")

## GFDL ----------------

get_time(data.path = "~/senior_thesis/combined_GFDL_files/",
         file.name = 'epc100_Omon_GFDL-ESM4_historical_r1i1p1f1_gr_185001-201412.nc')
get_time(data.path = "~/senior_thesis/combined_GFDL_files/",
         file.name = 'epc100_Omon_GFDL-ESM4_ssp585_r1i1p1f1_gr_201501-210012.nc')

time_series_100(model.name = "GFDL")

##IPSL -------------

get_time(data.path = "~/senior_thesis/combined_IPSL_files/",
         file.name = 'epc100_Omon_IPSL-CM6A-LR_historical_r1i1p1f1_gn_185001-201412.nc')
get_time(data.path = "~/senior_thesis/combined_IPSL_files/",
         file.name = 'epc100_Omon_IPSL-CM6A-LR_ssp585_r1i1p1f1_gn_201501-210012.nc')

time_series_100(model.name = "IPSL")

## MPI -------------

get_time(data.path = "~/senior_thesis/combined_MPI_files/",
         file.name = 'epc100_Omon_MPI-ESM1-2-HR_historical_r1i1p1f1_gn_185001-201412.nc')
get_time(data.path = "~/senior_thesis/combined_MPI_files/",
         file.name = 'epc100_Omon_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_201501-210012.nc')

time_series_100(model.name = "MPI")

## UKESM -------------

get_time(data.path = "~/senior_thesis/combined_UKESM_files/",
         file.name = 'epc100_Omon_UKESM1-0-LL_historical_r1i1p1f2_gn_185001-201412.nc')
get_time(data.path = "~/senior_thesis/combined_UKESM_files/",
         file.name = 'epc100_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_201501-210012.nc')

time_series_100(model.name = "UKESM")

```


2. Calculate globally integrated POC flux time series at MLDmax
    - first calculate time series MLDmax arrays
```{r}

setwd('~/senior_thesis/')
source('libraries.R')
source('get_time.R')
setwd('~/time_series_analysis/code/')
source('calc_time_series_MLDmax.R')
source('calc_time_series_expc.R')
source('calc_time_series_expc_UKESM.R')

## CESM ----------

get_time(data.path = "~/senior_thesis/combined_CESM_files/",
         file.name = 'mlotst_Omon_CESM2_historical_r10i1p1f1_gn_185001-201412.nc')
get_time(data.path = "~/senior_thesis/combined_CESM_files/",
         file.name = 'mlotst_Omon_CESM2_ssp585_r10i1p1f1_gn_201501-210012.nc')

time_series_MLDmax("CESM")

get_time(data.path = "~/senior_thesis/combined_CESM_files/",
         file.name = 'expc_Oyr_CESM2_historical_r10i1p1f1_gn_1850-2014.nc')
get_time(data.path = "~/senior_thesis/combined_CESM_files/",
         file.name = 'expc_Oyr_CESM2_ssp585_r10i1p1f1_gn_2015-2100.nc')

#calculating globally integrated POC flux at MLDmax from 1850-2100
time_series_expc(model.name = "CESM",
                 lon.length = 1:320,
                 lat.length = 1:384,
                 DH = "MLDmax")

## CM4 ---------------

get_time(data.path = "~/senior_thesis/combined_CM4_files/",
         file.name = 'mlotst_Omon_GFDL-CM4_historical_r1i1p1f1_gr_185001-201412.nc')
get_time(data.path = "~/senior_thesis/combined_CM4_files/",
         file.name = 'mlotst_Omon_GFDL-CM4_ssp585_r1i1p1f1_gr_201501-210012.nc')

time_series_MLDmax("CM4")

time_series_expc(model.name = "CM4",
                 lon.length = 1:360,
                 lat.length = 1:180,
                 DH = "MLDmax")

## CMCC --------------

get_time(data.path = "~/senior_thesis/combined_CMCC_files/",
         file.name = 'mlotst_Omon_CMCC-ESM2_historical_r1i1p1f1_gn_185001-201412.nc')
get_time(data.path = "~/senior_thesis/combined_CMCC_files/",
         file.name = 'mlotst_Omon_CMCC-ESM2_ssp585_r1i1p1f1_gn_201501-210012.nc')

time_series_MLDmax("CMCC")

get_time(data.path = "~/senior_thesis/combined_CMCC_files/",
         file.name = 'expc_Oyr_CMCC-ESM2_historical_r1i1p1f1_gn_1850-2014.nc')
get_time(data.path = "~/senior_thesis/combined_CMCC_files/",
         file.name = 'expc_Oyr_CMCC-ESM2_ssp585_r1i1p1f1_gn_2015-2100.nc')

#calculating globally integrated POC flux at MLDmax from 1850-2100
time_series_expc(model.name = "CMCC",
                 lon.length = 1:362,
                 lat.length = 1:292,
                 DH = "MLDmax")


## EC-Earth --------------

get_time(data.path = "~/senior_thesis/combined_EC-Earth_files/",
         file.name = 'mlotst_Omon_EC-Earth3-CC_historical_r1i1p1f1_gn_185001-201412.nc')
get_time(data.path = "~/senior_thesis/combined_EC-Earth_files/",
         file.name = 'mlotst_Omon_EC-Earth3-CC_ssp585_r1i1p1f1_gn_201501-210012.nc')

time_series_MLDmax("EC-Earth")

get_time(data.path = "~/senior_thesis/combined_EC-Earth_files/",
         file.name = 'expc_Oyr_MPI-ESM1-2-HR_historical_r1i1p1f1_gn_1850-2014.nc')
get_time(data.path = "~/senior_thesis/combined_EC-Earth_files/",
         file.name = 'expc_Oyr_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_2015-2100.nc')

#calculating globally integrated POC flux at MLDmax from 1850-2100
time_series_expc(model.name = "EC-Earth",
                 lon.length = 1:362,
                 lat.length = 1:292,
                 DH = "MLDmax")

## GFDL ------------------

get_time(data.path = "~/senior_thesis/combined_GFDL_files/",
         file.name = 'mlotst_Omon_GFDL-ESM4_historical_r1i1p1f1_gr_185001-201412.nc')
get_time(data.path = "~/senior_thesis/combined_GFDL_files/",
         file.name = 'mlotst_Omon_GFDL-ESM4_ssp585_r1i1p1f1_gr_201501-210012.nc')

time_series_MLDmax("GFDL")

get_time(data.path = "~/senior_thesis/combined_GFDL_files/",
         file.name = 'expc_Oyr_GFDL-ESM4_historical_r1i1p1f1_gr_1850-2014.nc')
get_time(data.path = "~/senior_thesis/combined_GFDL_files/",
         file.name = 'expc_Oyr_GFDL-ESM4_ssp585_r1i1p1f1_gr_2015-2100.nc')

#calculating globally integrated POC flux at MLDmax from 1850-2100
time_series_expc(model.name = "GFDL",
                 lon.length = 1:360,
                 lat.length = 1:180,
                 DH = "MLDmax")

## IPSL -------------

get_time(data.path = "~/senior_thesis/combined_IPSL_files/",
         file.name = 'mlotst_Omon_IPSL-CM6A-LR_historical_r1i1p1f1_gn_185001-201412.nc')
get_time(data.path = "~/senior_thesis/combined_IPSL_files/",
         file.name = 'mlotst_Omon_IPSL-CM6A-LR_ssp585_r1i1p1f1_gn_201501-210012.nc')

time_series_MLDmax("IPSL")

get_time(data.path = "~/senior_thesis/combined_IPSL_files/",
         file.name = 'expc_Oyr_IPSL-CM6A-LR_historical_r1i1p1f1_gn_1850-2014.nc')
get_time(data.path = "~/senior_thesis/combined_IPSL_files/",
         file.name = 'expc_Oyr_IPSL-CM6A-LR_ssp585_r1i1p1f1_gn_2015-2100.nc')

#calculating globally integrated POC flux at MLDmax from 1850-2100
time_series_expc(model.name = "IPSL",
                 lon.length = 1:362,
                 lat.length = 1:332,
                 DH = "MLDmax")

## MPI --------------------

get_time(data.path = "~/senior_thesis/combined_MPI_files/",
         file.name = 'mlotst_Omon_MPI-ESM1-2-HR_historical_r1i1p1f1_gn_185001-201412.nc')
get_time(data.path = "~/senior_thesis/combined_MPI_files/",
         file.name = 'mlotst_Omon_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_201501-210012.nc')

time_series_MLDmax("MPI")

get_time(data.path = "~/senior_thesis/combined_MPI_files/",
         file.name = 'expc_Oyr_MPI-ESM1-2-HR_historical_r1i1p1f1_gn_1850-2014.nc')
get_time(data.path = "~/senior_thesis/combined_MPI_files/",
         file.name = 'expc_Oyr_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_2015-2100.nc')

#calculating globally integrated POC flux at MLDmax from 1850-2100
time_series_expc(model.name = "MPI",
                 lon.length = 1:802,
                 lat.length = 1:404,
                 DH = "MLDmax")

##UKESM --------------

# special code because the files are too big to combine

setwd('~/senior_thesis/')
source('libraries.R')
source('get_time.R')
setwd('~/time_series_analysis/code/')
source('calc_time_series_expc_UKESM.R')

get_time(data.path = "~/senior_thesis/combined_UKESM_files/",
         file.name = 'mlotst_Omon_UKESM1-0-LL_historical_r1i1p1f2_gn_185001-201412.nc')
get_time(data.path = "~/senior_thesis/combined_UKESM_files/",
         file.name = 'mlotst_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_201501-210012.nc')

time_series_MLDmax("UKESM")

get_time(data.path = "~/senior_thesis/combined_UKESM_files/",
         file.name = 'expc_Omon_UKESM1-0-LL_historical_r1i1p1f2_gn_185001-189912.nc')
get_time(data.path = "~/senior_thesis/combined_UKESM_files/",
         file.name = 'expc_Omon_UKESM1-0-LL_historical_r1i1p1f2_gn_190001-194912.nc')
get_time(data.path = "~/senior_thesis/combined_UKESM_files/",
         file.name = 'expc_Omon_UKESM1-0-LL_historical_r1i1p1f2_gn_195001-199912.nc')
get_time(data.path = "~/senior_thesis/combined_UKESM_files/",
         file.name = 'expc_Omon_UKESM1-0-LL_historical_r1i1p1f2_gn_200001-201412.nc')
get_time(data.path = "~/senior_thesis/combined_UKESM_files/",
         file.name = 'expc_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_201501-204912.nc')
get_time(data.path = "~/senior_thesis/combined_UKESM_files/",
         file.name = 'expc_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_205001-210012.nc')

time_series_expc_UKESM(DH = "MLDmax", file = 1)
time_series_expc_UKESM(DH = "MLDmax", file = 2)
time_series_expc_UKESM(DH = "MLDmax", file = 3)
time_series_expc_UKESM(DH = "MLDmax", file = 4)
time_series_expc_UKESM(DH = "MLDmax", file = 5)
time_series_expc_UKESM(DH = "MLDmax", file = 6)

#combine UKESM files

setwd("~/senior_thesis/plotting_dataframes/time_series/expc_MLDmax/UKESM_uncombined/")
df.sep <- list.files(pattern = "UKESM")

#create empty list for storing for loop output
time.series <- list()

for(i in df.sep) {
  
  #read in csv file
  df <- read_csv(i)
  #store into list
  time.series[[i]] <- df
}

combined <- time.series %>%
  bind_rows

#delete duplicate year NA rows
combined <- combined[,-c(1)]

write_csv(combined, "~/time_series_analysis/files/POC_MLDmax/UKESM_time_series_expc_MLDmax.csv")

```


3. Calculate globally integrated time series at 1000m depth horizon
```{r}

setwd('~/senior_thesis/')
source('libraries.R')
source('get_time.R')
setwd('~/time_series_analysis/code/')
source('calc_time_series_expc.R')
source('calc_time_series_expc_UKESM.R')

#already checked time steps in the previous step

# CESM ---------

#calculating globally integrated POC flux at 1000m from 1850-2100
time_series_expc(model.name = "CESM",
                 lon.length = 1:320,
                 lat.length = 1:384,
                 DH = 1000)

# CM4 ---------

time_series_expc(model.name = "CM4",
                 lon.length = 1:360,
                 lat.length = 1:180,
                 DH = 1000)

# CMCC ------------

time_series_expc(model.name = "CMCC",
                 lon.length = 1:362,
                 lat.length = 1:292,
                 DH = 1000)

# EC-Earth -------------

time_series_expc(model.name = "EC-Earth",
                 lon.length = 1:362,
                 lat.length = 1:292,
                 DH = 1000)

# GFDL ----------------

time_series_expc(model.name = "GFDL",
                 lon.length = 1:360,
                 lat.length = 1:180,
                 DH = 1000)

#IPSL ------------

time_series_expc(model.name = "IPSL",
                 lon.length = 1:362,
                 lat.length = 1:332,
                 DH = 1000)

#MPI -----------

time_series_expc(model.name = "MPI",
                 lon.length = 1:802,
                 lat.length = 1:404,
                 DH = 1000)

#UKESM --------------

time_series_expc_UKESM(DH = 1000, file = 1)
time_series_expc_UKESM(DH = 1000, file = 2)
time_series_expc_UKESM(DH = 1000, file = 3)
time_series_expc_UKESM(DH = 1000, file = 4)
time_series_expc_UKESM(DH = 1000, file = 5)
time_series_expc_UKESM(DH = 1000, file = 6)

#combine UKESM files

setwd("~/senior_thesis/plotting_dataframes/time_series/expc_1000/UKESM_uncombined/")
df.sep <- list.files(pattern = "UKESM")

#create empty list for storing for loop output
time.series <- list()

for(i in df.sep) {
  
  #read in csv file
  df <- read_csv(i)
  #store into list
  time.series[[i]] <- df
}

combined <- time.series %>%
  bind_rows

write_csv(combined, "~/senior_thesis/plotting_dataframes/time_series/expc_1000/UKESM_time_series_expc_1000.csv")

```


4. Calculate POC flux at euphotic zone depth
    - calculate ez depth arrays first
```{r}

setwd("~/senior_thesis/")
source("libraries.R")
source("get_time.R")
setwd("~/time_series_analysis/code/")
source("calc_time_series_ez_depth.R")
source("calc_time_series_expc_ez.R")
source("calc_time_series_expc_UKESM.R")

#already checked expc time steps 

## CESM --------------

get_time(data.path = "~/senior_thesis/combined_CESM_files/",
         file.name = 'pp_Oyr_CESM2_ssp585_r10i1p1f1_gn_2015-2100.nc')
get_time(data.path = "~/senior_thesis/combined_CESM_files/",
         file.name = 'pp_Oyr_CESM2_historical_r10i1p1f1_gn_1850-2014.nc')

time_series_ez_depth(model.name = "CESM",
                     lon.length = 1:320,
                     lat.length = 1:384,
                     UKESM.file = NA)

time_series_expc_ez(model.name = "CESM",
                    lon.length = 1:320,
                    lat.length = 1:384)

## CM4 ------------

get_time(data.path = "~/senior_thesis/combined_CM4_files/", file.name = 'pp_Oyr_GFDL-CM4_historical_r1i1p1f1_gr_1850-2014.nc')
get_time(data.path = "~/senior_thesis/combined_CM4_files/", file.name = 'pp_Oyr_GFDL-CM4_ssp585_r1i1p1f1_gr_2015-2100.nc')

#this one is done at 10% max NPP
time_series_ez_depth(model.name = "CM4",
                     lon.length = 1:360,
                     lat.length = 1:180,
                     UKESM.file = NA)

time_series_expc_ez(model.name = "CM4",
                    lon.length = 1:360,
                    lat.length = 1:180)

## CMCC -----------

get_time(data.path = "~/senior_thesis/combined_CMCC_files/",
         file.name = 'pp_Omon_CMCC-ESM2_ssp585_r1i1p1f1_gn_201501-210012.nc')
get_time(data.path = "~/senior_thesis/combined_CMCC_files/",
         file.name = 'pp_Omon_CMCC-ESM2_historical_r1i1p1f1_gn_185001-201412.nc')

time_series_ez_depth(model.name = "CMCC",
                     lon.length = 1:362,
                     lat.length = 1:292,
                     UKESM.file = NA)

time_series_expc_ez(model.name = "CMCC",
                    lon.length = 1:362,
                    lat.length = 1:292)

## EC-Earth ---------

get_time(data.path = "~/senior_thesis/combined_EC-Earth_files/",
         file.name = 'pp_Oyr_EC-Earth3-CC_ssp585_r1i1p1f1_gn_2015-2100.nc')

#MISSING HISTORICAL DATA

time_series_ez_depth(model.name = "EC-Earth",
                     lon.length = 1:362,
                     lat.length = 1:292,
                     UKESM.file = NA)

time_series_expc_ez(model.name = "EC-Earth",
                    lon.length = 1:362,
                    lat.length = 1:292)

## GFDL ---------

get_time(data.path = "~/senior_thesis/combined_GFDL_files/", file.name = 'pp_Oyr_GFDL-ESM4_ssp585_r1i1p1f1_gr_2015-2100.nc')
get_time(data.path = "~/senior_thesis/combined_GFDL_files/", file.name = 'pp_Oyr_GFDL-ESM4_historical_r1i1p1f1_gr_1850-2014.nc')

time_series_ez_depth(model.name = "GFDL",
                     lon.length = 1:360,
                     lat.length = 1:180,
                     UKESM.file = NA)

time_series_expc_ez(model.name = "GFDL",
                    lon.length = 1:360,
                    lat.length = 1:180)

## IPSL ----------

get_time(data.path = "~/senior_thesis/combined_IPSL_files/", file.name = 'pp_Oyr_IPSL-CM6A-LR_ssp585_r1i1p1f1_gn_2015-2100.nc')
get_time(data.path = "~/senior_thesis/combined_IPSL_files/", file.name = 'pp_Oyr_IPSL-CM6A-LR_historical_r1i1p1f1_gn_1850-2014.nc')

time_series_ez_depth(model.name = "IPSL",
                     lon.length = 1:362,
                     lat.length = 1:332,
                     UKESM.file = NA)

time_series_expc_ez(model.name = "IPSL",
                     lon.length = 1:362,
                     lat.length = 1:332)

## MPI ----------

get_time(data.path = "~/senior_thesis/combined_MPI_files/", file.name = 'pp_Oyr_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_2015-2100.nc')
get_time(data.path = "~/senior_thesis/combined_MPI_files/", file.name = 'pp_Oyr_MPI-ESM1-2-HR_historical_r1i1p1f1_gn_1850-2014.nc')

time_series_ez_depth(model.name = "MPI",
                     lon.length = 1:802,
                     lat.length = 1:404,
                     UKESM.file = NA)

time_series_expc_ez(model.name = "MPI",
                     lon.length = 1:802,
                     lat.length = 1:404)

## UKESM ----------

get_time(data.path = "~/senior_thesis/combined_UKESM_files/", file.name = 'pp_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_201501-210012.nc')

#2015-2100
time_series_ez_depth(model.name = "UKESM",
                     lon.length = 1:360,
                     lat.length = 1:330,
                     UKESM.file = 5)

get_time(data.path = "~/senior_thesis/combined_UKESM_files/", file.name = 'pp_Omon_UKESM1-0-LL_historical_r1i1p1f2_gn_185001-189912.nc')

#1850-1899
time_series_ez_depth(model.name = "UKESM",
                     lon.length = 1:360,
                     lat.length = 1:330,
                     UKESM.file = 1)

get_time(data.path = "~/senior_thesis/combined_UKESM_files/", file.name = 'pp_Omon_UKESM1-0-LL_historical_r1i1p1f2_gn_190001-194912.nc')

#1900-1949
time_series_ez_depth(model.name = "UKESM",
                     lon.length = 1:360,
                     lat.length = 1:330,
                     UKESM.file = 2)

get_time(data.path = "~/senior_thesis/combined_UKESM_files/", file.name = 'pp_Omon_UKESM1-0-LL_historical_r1i1p1f2_gn_195001-199912.nc')

#1950-1999
time_series_ez_depth(model.name = "UKESM",
                     lon.length = 1:360,
                     lat.length = 1:330,
                     UKESM.file = 3)

get_time(data.path = "~/senior_thesis/combined_UKESM_files/", file.name = 'pp_Omon_UKESM1-0-LL_historical_r1i1p1f2_gn_200001-201412.nc')

#2000-2014
time_series_ez_depth(model.name = "UKESM",
                     lon.length = 1:360,
                     lat.length = 1:330,
                     UKESM.file = 4)

#calculate POC flux at ez depth time series
time_series_expc_UKESM(DH = "ez_depth", file = 1)
time_series_expc_UKESM(DH = "ez_depth", file = 2)
time_series_expc_UKESM(DH = "ez_depth", file = 3)
time_series_expc_UKESM(DH = "ez_depth", file = 4)
time_series_expc_UKESM(DH = "ez_depth", file = 5)
time_series_expc_UKESM(DH = "ez_depth", file = 6)

#combine UKESM files

setwd("~/senior_thesis/plotting_dataframes/time_series/expc_ez/UKESM_uncombined/")
df.sep <- list.files(pattern = "UKESM")

#create empty list for storing for loop output
time.series <- list()

for(i in df.sep) {
  
  #read in csv file
  df <- read_csv(i)
  #store into list
  time.series[[i]] <- df
}

combined <- time.series %>%
  bind_rows

write_csv(combined, "~/senior_thesis/plotting_dataframes/time_series/expc_ez/UKESM_time_series_expc_ez.csv")

```


5. Calculate POC flux at the PCD
```{r}

setwd("~/senior_thesis/")
source("libraries.R")
setwd("~/time_series_analysis/code/")
source("calc_time_series_expc.R")
source("calc_time_series_expc_UKESM.R")

#already checked time steps in the previous step

# CESM ---------

time_series_expc(model.name = "CESM",
                 lon.length = 1:320,
                 lat.length = 1:384,
                 DH = "PCD")

# CM4 -------------

time_series_expc(model.name = "CM4",
                 lon.length = 1:360,
                 lat.length = 1:180,
                 DH = "PCD")

# CMCC ------------

time_series_expc(model.name = "CMCC",
                 lon.length = 1:362,
                 lat.length = 1:292,
                 DH = "PCD")

# EC-Earth -------------

time_series_expc(model.name = "EC-Earth",
                 lon.length = 1:362,
                 lat.length = 1:292,
                 DH = "PCD")

# GFDL ----------------

time_series_expc(model.name = "GFDL",
                 lon.length = 1:360,
                 lat.length = 1:180,
                 DH = "PCD")

#IPSL ------------

time_series_expc(model.name = "IPSL",
                 lon.length = 1:362,
                 lat.length = 1:332,
                 DH = "PCD")

#MPI -----------

time_series_expc(model.name = "MPI",
                 lon.length = 1:802,
                 lat.length = 1:404,
                 DH = "PCD")

#UKESM --------------

time_series_expc_UKESM(DH = "PCD", file = 1)
time_series_expc_UKESM(DH = "PCD", file = 2)
time_series_expc_UKESM(DH = "PCD", file = 3)
time_series_expc_UKESM(DH = "PCD", file = 4)
time_series_expc_UKESM(DH = "PCD", file = 5)
time_series_expc_UKESM(DH = "PCD", file = 6)

#combine UKESM files

setwd("~/time_series_analysis/files/POC_PCD/UKESM_uncombined/")
df.sep <- list.files(pattern = "UKESM")

#create empty list for storing for loop output
time.series <- list()

for(i in df.sep) {
  
  #read in csv file
  df <- read_csv(i)
  #store into list
  time.series[[i]] <- df
}

combined <- time.series %>%
  bind_rows

write_csv(combined, "~/time_series_analysis/files/POC_PCD/UKESM_time_series_expc_PCD.csv")

```


6. Calculate globally integrated NPP time series (1850-2100)
```{r}

setwd("~/senior_thesis/")
source("libraries.R")
source("get_time.R")
setwd("~/time_series_analysis/code/")
source("calc_time_series_npp.R")

## CESM --------------

#Z length = 15
time_series_npp(model.name = "CESM",
                lon.length = 1:320,
                lat.length = 1:384)

# CM4 --------------

time_series_npp(model.name = "CM4",
                lon.length = 1:360,
                lat.length = 1:180)

## CMCC --------------

# v = 1:85 and 1:165
#Z length = 50
time_series_npp(model.name = "CMCC",
                lon.length = 1:362,
                lat.length = 1:292)

  
## EC-Earth -------------

#missing historical data
# v = 1:86
#Z length = 75
time_series_npp(model.name = "EC-Earth",
                lon.length = 1:362,
                lat.length = 1:292)

## GFDL ----------------

#v = 1:85 and 1:164
#Z length = 35
time_series_npp(model.name = "GFDL",
                lon.length = 1:360,
                lat.length = 1:180)

#IPSL ------------

#v = 1:86 1:165
#Z length = 75
time_series_npp(model.name = "IPSL",
                lon.length = 1:362,
                lat.length = 1:332)


#MPI -----------

#Z length = 40
time_series_npp(model.name = "MPI",
                lon.length = 1:802,
                lat.length = 1:404)

#UKESM ------------

setwd("~/senior_thesis/")
source("libraries.R")
source("get_time.R")
source("calc_time_series_npp_UKESM.R")


time_series_npp_UKESM(UKESM.file = 1)
time_series_npp_UKESM(UKESM.file = 2)
time_series_npp_UKESM(UKESM.file = 3)
time_series_npp_UKESM(UKESM.file = 4)
time_series_npp_UKESM(UKESM.file = 5)


#NOTE: Run this in a script, it doesn't work in the notebook for some reason
setwd("~/senior_thesis/plotting_dataframes/time_series/NPP/UKESM_uncombined/")
df.sep <- list.files(pattern = "UKESM")

#create empty list for storing for loop output
time.series <- list()

for(i in df.sep) {
  
  #read in csv file
  df <- read_csv(i)
  #store into list
  time.series[[i]] <- df
}

combined <- time.series %>%
  bind_rows

write_csv(combined, "~/senior_thesis/plotting_dataframes/time_series/NPP/UKESM_time_series_npp.csv")

```
